---
title: "HW2_315"
author: "Justin Song - jjs5874 - Scott - https://github.com/jujiwoo/HW3_315"
date: "2024-02-07"
output:
  pdf_document: default
  html_document: default
---

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.height=5, fig.width=10, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=100))
```

```{r, echo=FALSE, results='hide', message=FALSE}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(knitr)
library(mosaic)
creatine = read.csv('creatinine.csv')
market = read.csv('marketmodel.csv')
covid = read.csv('covid.csv')
milk = read.csv('milk.csv')

```

**Problem 1**

Part A
```{r, echo=FALSE}
model = lm(creatclear ~ age, data = creatine)
coef(model)
```

A creatine clearance rate expected of a 55 year old would be around 113 mL/minute. I determined this by utilizing the lm() function to find the least squares regression model. By finding the formula, y = -0.6198159x + 147.8129158, I was able to use it to find the expected "y-value" or the expected creatine clearance rate. 

Part B

The coefficient for the age term in the linear model is -0.6198159. This means that for each additional year of age, the creatinine clearance rate is expected to decrease by 0.6198159 ml/min.

Part C

```{r, echo=FALSE}
ggplot(creatine, aes(x=age, y=creatclear)) + 
  geom_point() + 
  geom_smooth(method='lm') + labs(title = "Relationship Between Age and Creatine Clearance", x = "Age", y="Creatine Clearance Rate")
```
A 40 year old with a rate of 135 versus a 60 year old with a rate of 112 differs through the fact of residual through the least square regressions model. An average 40 year old would have a rate of around 123 mL/minute while an average 60 year old would have a rate of around 110 mL/minute. Seeing that having a higher positive residual, (actual - predicted) means a person is healthier, shows that the 40 year old is healthier with a positive residual of around 135 - 123 = 12, than the 60 year old with a positive residual of around 112-110 = 2.

**Problem 2**

```{r, echo=FALSE}
AAPL = lm(AAPL ~ SPY, data = market)  
GOOG = lm(GOOG ~ SPY, data = market)
MRK = lm(MRK ~ SPY, data = market) 
JNJ = lm(JNJ ~ SPY, data = market)
WMT = lm(WMT ~ SPY, data = market)
TGT = lm(TGT ~ SPY, data = market)

market_tibble = tibble(
  Ticker = c("AAPL", "GOOG", "MRK", "JNJ", "WMT", "TGT"),
  Intercept = c(coef(AAPL)[1], coef(GOOG)[1], coef(MRK)[1], coef(JNJ)[1], coef(WMT)[1], coef(TGT)[1]),
  Slope = c(coef(AAPL)[2], coef(GOOG)[2], coef(MRK)[2], coef(JNJ)[2], coef(WMT)[2], coef(TGT)[2]),
  RSquared = c(rsquared(AAPL), rsquared(GOOG), rsquared(MRK), rsquared(JNJ), rsquared(WMT), rsquared(TGT))
)


kable(market_tibble, caption = "Table 1. Regression of individual stock returns against S&P 500 returns. The table shows the beta coefficient, which measures the stock's sensitivity to market returns, and the R-squared value, which measures the proportion of variance explained by the market.")

```
The beta of a stock is a measure of how sensitive the stock's returns are to movements in the overall market. It captures how much a stock tends to go up or down when the market goes up or down. Beta is calculated by running a linear regression between the stock's returns and the market's returns. Mathematically, this regression takes the form:

Rstock = Alpha + Beta * Rmarket + error

Where Rstock is the stock's return, Rmarket is the market's return, and Beta is the slope coefficient. Intuitively, Beta tells us how much the stock return changes for a 1 unit change in the market return. A stock with Beta = 1.5 tends to move 1.5% when the market moves 1%.
Stocks with Beta > 1 are more volatile and sensitive to the market than average. These high-beta stocks tend to outperform the market when it is going up but also fall faster when it is going down. Stocks with Beta < 1 are less sensitive and tend to be more stable. Low-beta stocks underperform in bull markets but provide more downside protection in bear markets.
By regressing a stock's historical returns against a market benchmark, we can estimate the stock's Beta. This helps understand how sensitive the stock is to swings in the overall market. Beta is a key input in models like the Capital Asset Pricing Model that are used to evaluate asset prices and expected returns. In summary, a stock's Beta captures the slope relationship between the stock and market returns. It is a metric of volatility and systematic risk calculated using linear regression. Beta is widely used in finance to model and evaluate asset returns.


Based on the regression analysis, WMT has the lowest systematic risk among the six stocks analyzed. WMT has the lowest beta at 0.519, indicating it has the least sensitivity to movements in the overall market.

AAPL has the highest systematic risk with a beta of 1.066, making it the most volatile and market-sensitive of the stocks. The high beta implies AAPL's returns tend to fluctuate more than the market during ups and downs.

**Problem 3**

```{r, echo=FALSE}
italy = covid[covid$country == "Italy",] 

lm_italy = lm(log(deaths) ~ days_since_first_death, data=italy)
coef(lm_italy)

doubling_time_italy = log(2)/coef(lm_italy)[2] 

spain = covid[covid$country == "Spain",]

lm_spain = lm(log(deaths) ~ days_since_first_death, data=spain)

doubling_time_spain = log(2)/coef(lm_spain)[2] 

data = rbind(italy, spain)

ggplot(data, aes(x = days_since_first_death, y = log(deaths), color=country)) +
  geom_line() +
  geom_abline(data=italy, aes(intercept = coef(lm_italy)[1], slope = coef(lm_italy)[2]), color='red') +
  geom_abline(data=spain, aes(intercept = coef(lm_spain)[1], slope = coef(lm_spain)[2]), color='blue') + labs(x= "Days Since First Death", title= "Covid-19 Death Growth Rates for Italy and Spain")

```

The estimated growth rate and doubling time for Italy is `r round(coef(lm_italy)[2],3)` and `r round(doubling_time_italy)`. The estimated growth rate and doubling time for Italy is `r round(coef(lm_spain)[2],3)` and `r round(doubling_time_spain)`. 

**Problem 4**

```{r, echo=FALSE}

ggplot(milk) +
   geom_point(aes(x=log(price), y=log(sales)))
lm_milk = lm(log(sales) ~ log(price), data=milk)
coef(lm_milk)

```
The estimated elasticity is about -1.62. The estimated elasticity suggests that a 1% increase in the price of milk corresponds to a decrease in consumer demand of approximately 1.62%. I found this by realizing this problem dealt with power law, therefore I had to graph the plot in such a way that it becomes linear. By making log(x) and log(y), the graph becomes more linear, showing that our ending fitted line is y = -1.618578x + 4.720604.  









